Deep Learning for Automatic Speech Recognition

### 2015-05-01 Paper/Paper.tex
Last round of edits

where $\inAngle{ \cdot }_\text{1}$ is a single step Gibbs sampled expectation. These terms are expectations in which nodes $i$ and $j$ active simultaneously given the training data and model. Given this insight, regular stochastic gradient descent can be performed and the parameters of a RBM fitted to training data.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. As mentioned above, they do see some slight improvements in the LWS scheme. They do not explain their hardware resources or how long their training time took. Yet for a little perspective, in \cite{hau2011exploring} they used a somewhat similarly structured CNN which required less than a day to train. Their's is less complicated than the one present in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, so slightly longer training times would not be surprising.

@@

Comparison of automatic speech recognition system consists of three principle error metrics: sentence (SER), word (WER), and phoneme (PER) error rates. These look at the ratio of incorrect entities to the number of total entities with the exception of word error rate which uses a Levenshtein approach to measure the number of insertions, substitutions, and deletions. A sentence is considered incorrect if there is at least one incorrect word.

>>>>

where $\inAngle{ \cdot }_\text{1}$ is a single step Gibbs sampled expectation. These terms are expectations in which nodes $i$ and $j$ are simultaneously active given the training data and model. Given this insight, regular stochastic gradient descent can be performed and the parameters of a RBM fitted to training data.

@@

\cite{DBLP:journals/taslp/Abdel-HamidMJDPY14} use just one convolution and pooling ply, and two 1000 unit, fully connected hidden layers in their experimental section. They also make use of 150 feature maps for full weight sharing, and 80 feature maps for limited weight sharing. As mentioned above, they do see some slight improvements in the LWS scheme. They do not explain their hardware resources or how long their training time took. Yet for a little perspective, in \cite{hau2011exploring} they used a somewhat similarly structured CNN which required less than a day to train. Theirs is less complicated than the one present in \cite{DBLP:journals/taslp/Abdel-HamidMJDPY14}, so slightly longer training times would not be surprising.

@@

Comparison of automatic speech recognition system consists of three principle error metrics: sentence (SER), word (WER), and phoneme (PER) error rates. These look at the ratio of incorrect entities to the number of total entities with the exception of word error rate which uses a Levenshtein approach to measure the number of insertions, substitutions, and deletions relative to the total number of words. A sentence is considered incorrect if there is at least one incorrect word.
